A self-consistency check for unitary propagation of Hawking quanta

### 2016-11-05 Draft_BH_shells.tex
Grammar check and updated fig 3

\begin{abstract}
The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
Instead of invoking conjectural quantum-gravity effects to modify such assumption, we propose a self-consistency check.
We establish an analogy to Feynman's analysis of a double-slit experiment. 
Feynman showed that a unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen the interference pattern is projected onto goes to infinitely far away.
We argue for an analogous self-consistency check for quantum field theory in curved spacetime.
We apply it to the propagation of Hawking quanta and test whether ignoring the entanglement with the geometry also becomes arbitrarily reliable in the limit of a large black hole. 
We present curious results to suggest a negative answer, and we discuss how this loss of na\"ive unitarity in QFT might be related to a solution of the paradox based on the soft-hair-memory effect.
\end{abstract}

@@

Before presenting our argument, we will first explain its relation to some existing ideas.
The recent paper by Osuga and Page \cite{OsuPag16} provides an abstract framework of how modifying Statement Three resolves the paradox.
Basically, the near horizon mode is thermal as demanded by Statement Two.
However, it propagates out in a non-unitary process, gaining the appropriate information to restore the unitary $S$-matrix demanded by Statement One. 
For this abstract model to work in practice, this non-unitary propagation should be understood as interaction with a hidden system.
Here hidden simply means something that a na\"ive application of local QFT is ignorant to.
The obvious candidate of such hidden system is the geometry.

@@

\begin{figure}[tb]
\begin{center}
\includegraphics[scale = 0.6]{Propertime.pdf}
\caption{The two parts of this diagrams describe two different scenarios. The trajectories of the photon are the lines in orange. The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines. The bottom part is a general case of two Hawking photons coming from a distance $r_e$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$. The top part shows two Hawking photons coming from the same distance $r_e$ from a black hole of mass $M$. Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $\Delta M, -\Delta M$ at $r_{1}, r_{2}$ respectively. The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M+\Delta M$.}
\label{fig-setup}
\end{center}
\end{figure}

@@

\item \textbf{Far from horizon ($M \ll l$)}: 
If we send signals from the Earth surface to somewhere far in the space, this result tell us how much can we trust a unitary QFT description.
It starts to show a small deviation from the Minkowski result, but in the $M \ll r_1$ limit, it is almost indistinguishable.

>>>>

\begin{abstract}
The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
Instead of invoking conjectural quantum-gravity effects to modify such an assumption, we propose a self-consistency check.
We establish an analogy to Feynman's analysis of a double-slit experiment. 
Feynman showed that unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen upon which the interference pattern is projected is infinitely far away.
We argue for an analogous self-consistency check for quantum field theory in curved spacetime.
We apply it to the propagation of Hawking quanta and test whether ignoring the entanglement with the geometry also becomes arbitrarily reliable in the limit of a large black hole. 
We present curious results to suggest a negative answer, and we discuss how this loss of na\"ive unitarity in QFT might be related to a solution of the paradox based on the soft-hair-memory effect.
\end{abstract}

@@

Before presenting our argument, we will first explain its relation to some existing ideas.
The recent paper by Osuga and Page \cite{OsuPag16} provides an abstract framework of how modifying Statement Three resolves the paradox.
Basically, the near horizon mode is thermal as demanded by Statement Two.
However, it propagates out in a non-unitary process, gaining the appropriate information to restore the unitary $S$-matrix demanded by Statement One. 
For this abstract model to work in practice, this non-unitary propagation should be understood as an interaction with a hidden system.
Here hidden simply means something that a na\"ive application of local QFT is ignorant to.
The obvious candidate of such hidden system is the geometry.

@@

\begin{figure}[tb]
\begin{center}
\includegraphics[scale = 0.6]{Propertime.pdf}
\caption{The two parts of this diagrams describe two different scenarios. The trajectories of the photon are the lines in orange. The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines. The bottom part is a general case of two Hawking photons coming from a distance $r_e$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$. The top part shows two Hawking photons coming from the same distance $r_e$ from a black hole of mass $M$. Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $\Delta M, -\Delta M$ at $r_{1}, r_{2}$ respectively. The region $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M+\Delta M$. The proper distance from the position where the photon is emitted to the position of the first shell is given by $l$ and the proper distance between the shells is given by $\Delta l$. }
\label{fig-setup}
\end{center}
\end{figure}

@@

\item \textbf{Far from horizon ($M \ll l$)}: 
If we send signals from the Earths' surface to somewhere far in the space, this result tell us how much can we trust a unitary QFT description.
It starts to show a small deviation from the Minkowski result, but in the $M \ll r_1$ limit, it is almost indistinguishable.
